Title

### 2013-03-22 inc/hardware/magnetic_lenses/maglens.tex
further tweaks to magnetic lenses

\begin{figure}
  \centering
  \input{polepiece-schematic}
  \caption[Side-view schematic of a shielded magnetic lens with a pole-piece]{
    Side-view schematic of a shielded magnetic lens with a pole-piece.
    The windings (current loops) are contained within the shielding.
    The magnetic field created by these windings is contained inside the shielding except in the gap.
  }
  \label{fig:polepiece-schematic}
\end{figure}

@@

%TODO need a description of the steel inner tube causing an effective diameter larger than the actual bore
For the UEM, I chose a bore diameter $D=2R=$0.5in and a pole-piece gap $S$=0.1in, for an ratio $S/D=0.2$.
By their table 8.2a this results in $\beta=0.0146$. Then, to create a focal length of 4in ($f/R=16$) table 8.13 gives a value for $k^2 \approx 0.06$.
Finally substituting this value into \ref{eq:elkareh_k2}, with $V=30$kV ($V_r\approx30.88$kV), one can deduce that $NI\approx356$A.

@@

\begin{figure}
  \centering
  \includegraphics{maglens.jpg}
  \caption[Side-view picture of the employed two custom large-bore magnetic lenses]{
    Side-view of the two custom large-bore magnetic lenses designed and built at UIC, seen installed in the prototype UEM.
    The coils are visible as is high permeability shielding used for the pole-piece.
    The outer (larger) plates and struts are for structural integrity only.
  }
  \label{fig:maglens-pic}
\end{figure}

\subsection{Thermal Properties}

@@

\begin{figure}
  \centering
  \input{polepiece-design}
  \caption[Side-view schematic of a shielded magnetic lens with a pole-piece]{
    Side-view schematic of a shielded magnetic lens with a pole-piece.
    The windings (current loops) are contained within the shielding.
    The magnetic field created by these windings is contained inside the shielding except in the gap.
  }
  \label{fig:polepiece-design}
\end{figure}

>>>>

\begin{figure}
  \centering
  \input{polepiece-schematic}
  \caption[Schematic of a generic magnetic lens with a pole-piece]{
    Side-view schematic of a generic magnetic lens with a pole-piece.
    The windings (current loops) are contained within the shielding.
    The magnetic field created by these windings is contained inside the shielding except in the gap.
  }
  \label{fig:polepiece-schematic}
\end{figure}

@@

\begin{figure}
  \centering
  \input{polepiece-design}
  \caption[Design schematic of our magnetic lens with a pole-piece]{
    Side-view schematic of the magnetic lens with a pole-piece designed for the UEM at UIC.
    On the center axis is the inner drift tube, with pole-piece gap separation disk.
    The end pieces are shown top and bottom.
    One bridge piece is shown detached (left) and one attached (right).
    Note that this figure is not drawn to the scale of the lenses at UIC, but rather to match the general schematic in \ref{fig:polepiece-schematic}.
  }
  \label{fig:polepiece-design}
\end{figure}

\ref{fig:polepiece-design} shows a simplistic design schematic of the lens designed and built for the UEM at UIC.
The central bore is a tube of stainless steel having a magnetic permeability of 1; this behaves magnetically as if it is not involved in the field shaping.
In this way the inner bore of the tube is in vacuum with minimal welding necessary.
The outer diameter of tube is milled down to an outer diameter of $D=2R=$0.5in, though a disk of larger diameter, and length $S$=0.1in, is left at the midpoint, which will separate the shielding material and be the pole-piece gap.

The high magnetic permeability shielding is in eleven pieces.
There are two end pieces end pieces are revolution solid of ``L'' profile.
These ends are slid together touching the disk at the midpoint of the drift tube; the disk is of the proper outer diameter to match the sheilding's smaller outer diameter.
The combination of the two ends and this disk make a ``U'' shape which contains the windings.

The top side of the end's larger outer side is flattend on eight sides.
These are the mount points for eight bridge pieces which connect the ends, completing the field-capturing shielding loop.
The gaps between the shielding bridges also allow for direct air cooling of the magnetic coils (see Section \ref{sec:mag_lens_thermal}).

I chose drift tube outer diameter to be $D=$0.5in and a pole-piece gap $S$=0.1in, for an ratio $S/D=0.2$.
By their table 8.2a this results in $\beta=0.0146$. Then, to create a focal length of 4in ($f/R=16$) table 8.13 gives a value for $k^2 \approx 0.06$.
Finally substituting this value into \ref{eq:elkareh_k2}, with $V=30$kV ($V_r\approx30.88$kV), one can deduce that $NI\approx356$A.

@@

\begin{figure}
  \centering
  \includegraphics{maglens.jpg}
  \caption[Side-view picture of the employed two custom large-bore magnetic lenses]{
    Side-view of the two custom large-bore magnetic lenses designed and built at UIC, seen installed in the prototype UEM.
    The coils are visible in the gaps between the high permeability shielding ``bridges''.
    The bridges are attached to the tops of the end pieces by bolts to complete the shielding loop.
    The outer (larger) plates and struts are for structural integrity only.
  }
  \label{fig:maglens-pic}
\end{figure}

\subsection{Thermal Properties} \label{sec:mag_lens_thermal}

@@
